---
title: "Social Network Analysis Assignment 1"
output:
  pdf_document: default
  html_notebook: default
---

# Question 1 

**Read in the file “sample_generated_network.csv”, located on Canvas. For the trust network, reproduce a plot similar to the one shown in class, showing the ties between individuals, their strength, and their direction. Exclude individuals who did not respond to the survey and who did not receive a complete set of responses about themselves from other students, but include everyone else.** 


Before importing the data, I inspect it at Excel. I found that two columns contains lots of blank values, thus I deleted them. Then I found the names of several columns don't appear at row names, then I deleted those columns. The final data contains 30 individuals. 


```{r}
rm(list = ls(all = TRUE))
library(igraph)
library(data.table)
setwd("C:/Users/cyma9/Dropbox/SocialNetwork/week1")
data = fread(file="sample_generated_network_new.csv", header = TRUE, stringsAsFactors=FALSE)

column_wise_replace = function(DT, x, y) {
	for(i in seq_along(x)){
		 for (j in seq_len(ncol(DT))){
   		set(DT,which(DT[[j]] == x[i]),j,y[i])
		}
	}
}




data = data[sample(nrow(data), replace = FALSE),]
advice = data[,(ncol(data) - 4):ncol(data)]
namekey = data[,1]

data = data[,2:(ncol(data) - 5)]

setcolorder(data, sample(colnames(data), replace = FALSE))

data = cbind(namekey, data, advice)


# make the choice data numeric
scale = cbind(c("Extremely Distrust  1","Distrust  2","Slightly Distrust  3","Neither Distrust Nor Trust  4", "Slightly Trust  5","Trust  6", "Extremely Trust  7", "I don't know this person.", "This is my own name."), c(-3, -2, -1, 0, 1, 2, 3, 0, 0))

column_wise_replace(data, scale[,1], scale[,2])

# make adjacency matrix

# subset to just the trust choices, then sort on the columns and rows to make each entry match up
# data are directed, so matrix will not be symmetric
adj = as.data.frame(data[,1:(ncol(data) - 5)])
rownames(adj) = adj[,1]
adj = adj[,-1]

adj = adj[sort(rownames(adj)),sort(colnames(adj))]

trusting = adj
trusting[trusting==-3] = 0
trusting[trusting==-2] = 0
trusting[trusting==-1] = 0

trusting = graph.adjacency(as.matrix(trusting), "directed", weighted = TRUE)


plot.igraph(trusting,vertex.label=NA,layout=layout.fruchterman.reingold, vertex.label.color="black",edge.width=E(trusting)$weight,vertex.size = 12, edge.arrow.size=.3,edge.curved=FALSE)

```

# Question 2 

```{r}
distrust = adj
distrust[distrust == 3] = 0
distrust[distrust == 2] = 0
distrust[distrust == 1] = 0
distrust[distrust == -3] = 3
distrust[distrust == -2] = 2
distrust[distrust == -1] = 1 
distrust_num = apply(distrust,2,as.numeric)
dev = colSums(distrust_num)
pal <- rainbow(max(dev) - min(dev) + 1 , alpha=.5)

distrust_graph = graph.adjacency(as.matrix(distrust_num), "directed", weighted = TRUE)
distrust_graph = set.vertex.attribute(distrust_graph, "dev", index = V(distrust_graph), dev) 
col = rep(0,30)
for ( i in c(1:30))
{
  col[i] = pal[dev[i] + 1]
}

plot.igraph(distrust_graph,vertex.label=NA,layout=layout.fruchterman.reingold, vertex.color = col, vertex.label.color="black",edge.width=E(distrust_graph)$weight,vertex.size = 12, edge.arrow.size=.3,edge.curved=FALSE)


```



# Question 3 
```{r}



count = rep(0,38)

advice_edge1 = cbind(data[,1], data$V38)
for(i in c(1:30))
  {
  count[data$V38[i]] =  count[data$V38[i]] + 1   
  }

advice_edge2 = cbind(data[,1], data$V39)
for(i in c(1:30))
{
  count[data$V39[i]] =  count[data$V39[i]] + 1   
}

advice_edge3 = cbind(data[,1], data$V40)
for(i in c(1:30))
{
  count[data$V40[i]] =  count[data$V40[i]] + 1   
}

advice_edge4 = cbind(data[,1], data$V41)
for(i in c(1:30))
{
  count[data$V41[i]] =  count[data$V41[i]] + 1   
}

advice_edge5 = cbind(data[,1], data$V42)
for(i in c(1:30))
{
  count[data$V42[i]] =  count[data$V42[i]] + 1   
}
print(count)
advice_edges = rbind(advice_edge1, advice_edge2, advice_edge3, advice_edge4, advice_edge5)

advice_seeking = graph.data.frame(advice_edges, directed = TRUE)
for ( i in c(1:35))
{
  V(advice_seeking)$color[i] = 'grey'
  if (V(advice_seeking)$name[i] == which.max(count))
  {
    V(advice_seeking)$color[i] = 'red'
  }
}

plot.igraph(advice_seeking,vertex.label=NA,layout=layout.fruchterman.reingold, vertex.label.color="black",edge.color="black",vertex.size = 12, edge.arrow.size=.3,edge.curved=FALSE)

```


# Question 4 
**How many of the relationships are reciprocated in each of the three networks? Do you think that this is more or less than would be reciprocated by random chance? Treat the trust and distrust relationships as binary. Perform this calculation directly on the matrices.**


```{r}


# trust
count_trust = 0 
for (i in c(1:30))
{
  for (j in c(1:30))
  {
    if ((adj[i,j]>0)&(adj[j,i]>0)){
      count_trust = count_trust + 1 
      
    }
  }
}

count_distrust = 0 
for (i in c(1:30))
{
  for (j in c(1:30))
  {
    if ((adj[i,j]<0)&(adj[j,i]<0)){
      count_distrust = count_distrust + 1 
      
    }
  }
}


advice_adj = matrix(0,nrow = 37, ncol = 37)
for ( i in c(1:nrow(advice_edges)))
{
  x = advice_edges[i]$`To begin, please select your name.`
  y = advice_edges[i]$V2
  advice_adj[x,y] = 1
}
count_advice = 0
for ( i in c(1:37))
{
  for ( j in c(1:37))
    if ((advice_adj[i,j]==1)&(advice_adj[j,i]==1))
    {
      count_advice = count_advice + 1
    }
}

print('How many of the trust relationships are reciprocated?')
print(count_trust)
print('How many of the distrust relationships are reciprocated?')
print(count_distrust)
print('How many of the seeking advice relationships are reciprocated?')
print(count_advice)





```

# Question 5 
**How many of the relationships in the trust network also exist in the advice network? How many of the relationships in the distrust network also exist in the advice network? Do you think this is surprising? Exclude individuals who did not respond to the survey and who did not receive a complete set of responses about themselves from other students, but include everyone else. Treat the trust and distrust relationships as binary. Perform this calculation directly on the matrices.**

```{r}


count_advice_trust = 0
count_advice_distrust = 0

for (i in c(1:30))
{
  for (j in c(1:30))
  {
    x = as.numeric(colnames(adj)[i])
    y = as.numeric(rownames(adj)[j])
    if ((adj[i,j]>0) & (advice_adj[x,y]>0))
    {
      count_advice_trust = count_advice_trust + 1
    }
    if ((adj[i,j]<0) & (advice_adj[x,y]>0))
    {
      count_advice_distrust = count_advice_distrust + 1
    }
    
  }
}
print('How many of the relationships in the trust network also exist in the advice network?')
print(count_advice_trust)

print('How many of the relationships in the distrust network also exist in the advice network?')
print(count_advice_distrust)



```


# Extra Question

```{r}
trusting = adj
trusting[trusting==-3] = 0
trusting[trusting==-2] = 0
trusting[trusting==-1] = 0

trusting_extra = graph.adjacency(as.matrix(trusting), "directed", weighted = TRUE)
E(trusting_extra)$color = 'green'

# plot.igraph(trusting_extra,vertex.label=NA,layout=layout.fruchterman.reingold, vertex.label.color="black",edge.width=E(trusting_extra)$weight,vertex.size = 12, edge.arrow.size=.3,edge.curved=FALSE)





distrust = adj
distrust[distrust == 3] = 0
distrust[distrust == 2] = 0
distrust[distrust == 1] = 0
distrust[distrust == -3] = 3
distrust[distrust == -2] = 2
distrust[distrust == -1] = 1 


distrust_graph_extra = graph.adjacency(as.matrix(distrust_num), "directed", weighted = TRUE)
E(distrust_graph_extra)$color  = 'red'


# plot.igraph(distrust_graph_extra,vertex.label=NA,layout=layout.fruchterman.reingold, vertex.label.color="black",edge.width=E(distrust_graph_extra)$weight,vertex.size = 12, edge.arrow.size=.3,edge.curved=TRUE)


extra_graph = union(distrust_graph_extra, trusting_extra) 
E(extra_graph)$color <- ifelse(is.na(E(extra_graph)$color_1),E(extra_graph)$color_2,E(extra_graph)$color_1)
E(extra_graph)$weight <- ifelse(is.na(E(extra_graph)$weight_1),E(extra_graph)$weight_1,E(extra_graph)$weight_2)


advice_adj_extra = adj

for (i in c(1:30))
{
  for (j in c(1:30))
  {
    x = as.numeric(colnames(adj)[i])
    y = as.numeric(rownames(adj)[j])
    if (advice_adj[x,y] == 1) 
    {
      advice_adj_extra[i,j] = 1
    }
    else
    {
      advice_adj_extra[i,j] = 0 
    }
  }
}

advice_graph_extra = graph.adjacency(as.matrix(advice_adj_extra), "directed", weighted = TRUE)
E(advice_graph_extra)$color  = 'black'











advice_edge = as_edgelist(advice_graph_extra, names = T)
trust_edge = as_edgelist(extra_graph, names = T)
new_edge = rbind(trust_edge, advice_edge)
graph_new = graph_from_edgelist(new_edge)

for (i in c(1:424))
{
  E(graph_new)$color[i] = E(extra_graph)$color[i]
  E(graph_new)$weight[i] = E(extra_graph)$weight[i]
}

for (i in c(425:554))
{
  E(graph_new)$color[i] = E(advice_graph_extra)$color[i-424]
  E(graph_new)$weight[i] = E(advice_graph_extra)$weight[i-424]
}


plot.igraph(graph_new,vertex.label=NA,layout=layout.fruchterman.reingold, vertex.label.color="black", edge.width=E(graph_new)$weight,edge.color = E(graph_new)$color,vertex.size = 12, edge.arrow.size=.3,edge.curved=TRUE)


```